Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
rewording experiment execution details

%frame this in the sense that we are saying, ``we have this figued out. we want feedback on other things.''
\noindent {\bfseries Experiment Execution Details} 
We plan to recruit around 150 users for the purpose of this study. This makes it largest user study to date on Tor (check this) This study will be performed at the Experimental Social Science Laboratory (Xlab) at the University of California, Berkeley. The laboratory space consists of 36 laptops with cubicle walls separating each laptop. We used individual host firewalls to simulate the censorship environments. We plan to write a browser extension to measure when users visit what websites in order to log which websites they were successfully able to visit. The total length of the experiment should be less than an hour. Participants will be compensated \$30 for their time, which is more to cover minimum wage and transportation costs.  \\

>>>>

%frame this in the sense that we are saying, ``we have this figued out. we want feedback on other things.''
\noindent {\bfseries Experiment Execution Details} 
We plan to recruit up to 200 users for the purpose of this study, 
making it largest user study to date examining Tor (check this). 
This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
the censorship environments and will write a browser extension to 
log when user activity, such as what websites they were successfully able to visit. 
The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take less than an hour. 
Participants will be compensated \$30 for their time, 
which is more to cover minimum wage and transportation costs.  \\
